Numerical simulation of the Cordilleran ice sheet through the last glacial cycle

### 2014-06-03 cordillera-cycle.tex
Improve results using Irina's suggestions.

Despite large differences in the input temperature offset time-series, the
model output presents consistent features that can be observed across the range
of forcing data used. In all simulations, ice cover is relatively restricted
during most of the glacial cycle, while two major glaciation events occur
during MIS~4 (61.9--55.4\,\unit{kyr}) and MIS~2 (29.5--16.9\,\unit{kyr},
Fig.~\ref{fig:timeseries}). A local ice minimum is consistently attained in between these
two events during MIS~3 (52.2--45.6\,\unit{kyr}).

However, the magitude and timing of these events vary significantly
between our simulations. For instance, the use of GRIP and NGRIP forcing
results in highest variability in modelled ice volume. Simulations driven by
the Antarctic and GRIP records reach a last glacial maximum in ice volume at
19.5--16.9\,\unit{kyr}, while simulations driven by oceanic records
and the NGRIP record attain it prior to 20.0\,\unit{kyr}.

Despite the different timing,
snapshots of model output show relatively consistent patterns of glaciation
(Fig.~\ref{fig:snapshots}). In all simulations, a central ice cap persists over
the Skeena mountains between the two glaciation events. However, the size of
this ice cap, as well as the magnitude of the MIS~4, depends sensitively on the temperature
offset time-series used to drive the model.

The modelled last glacial maximum ice sheet possess a central divide located at
about 3\,500\,\unit{m} elevation along the spine of the Rocky Mountains. The
distribution of surface velocities shows a clear asymmetry between the
maritime, western flank, and the continental, eastern flank of the ice sheet
(Fig.~\ref{fig:lgm}).

>>>>

Despite large differences in the input temperature offset time-series, the
model output presents consistent features that can be observed across the range
of forcing data used. In all simulations, total ice volume is relatively low
during most of the glacial cycle, while two major glaciation events occur
during MIS~4 (61.9--55.4\,\unit{kyr}) and MIS~2 (29.5--16.9\,\unit{kyr},
Fig.~\ref{fig:timeseries}). A local ice minimum is consistently attained in
between these two events during MIS~3 (52.2--45.6\,\unit{kyr}).
However, the magnitude and timing of these events vary significantly
between our simulations.

Simulations forced by the Greenland ice core records (GRIP, NGRIP) produce
highest variability in modelled ice volume throughout the glaciation history.
Although simulations forced by the Antarctic (EPICA, Vostok) and GRIP records
reach the last glacial maximum in ice volume at 19.5--16.9\,\unit{kyr}, those
driven by oceanic (ODP~1012, ODP~1020) and the NGRIP record attain it several
thousands of years earlier. The NGRIP record is the only temperature forcing
that predicts a more extensive glaciation during MIS~4 than at the LGM.

Simulations forced by oceanic and Antarctic records generally result in lower
modelled ice volume during MIS~4 and larger ice volume during MIS~3, thus lower
ice volume variability throughout the simulation length. The ODP~1012
record-driven simulation predicts rapid deglaciation prior to 20\,\unit{kyr}
before present due to a local temperature maximum inconsistent with all other
temperature forcing time series used. The ODP~1012 record-driven simulation
predicts an early last glacial volume maximum, followed by slower deglaciation
than modelled using other records. Finally, simulations forced by Antarctic ice
core records produce a continuous, rapid deglaciation after the last glacial
maximum, whereas the simulations driven by the GRIP records produce a rapid
deglaciation in three steps, including a glacial re-advance around the Younger
Dryas event.

Despite the different timing, snapshots of model output show relatively
consistent patterns of glaciation (Fig.~\ref{fig:snapshots}). As a result of
the different scaling factors applied to palaeo-temperature proxy records, the
ice sheet geometry at the last glacial maximum appears very similar from one
simulation to the next, including a central divide located at about
3\,500\,\unit{m} elevation along the spine of the Rocky Mountains. In all
simulations, a central ice cap persists over the Skeena mountains during MIS~3
between the two glaciation events. However, the size of this ice cap, as well
as the magnitude of the MIS~4 glaciation, depends sensitively on the choice of
palaeo-temperature proxy record used to drive the model.
